Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2022-03-04 results.tex
added notes after meeting Michal

Do we really need to compute the vacuum case numerically? We should be able to do it analytically, right?

\begin{figure}
\centering
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_time.png}
\caption{Time-to-solution for arginine with a constant permittivity. %(1) fix title, (2) can we put them in a single plot, (3) 
maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
\label{fig:arg_contant_time}
\end{figure}

@@

We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS for comparison. 
As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, however, the solvent permittivity was set to $\epsilon$=2. 
Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff [Alexov]. 
We did not consider a cutoff in our calculations, but this does not affect our validation exercise.

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
&Mesh size & $\Delta G_{solv}$\\
&\AA       &  kcal/mol \\
\hline
\multirow{3}{*}{APBS}& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
&0.26$\times$0.26$\times$0.26 & -32.3375\\ 
&0.17$\times$0.17$\times$0.17 & -32.3413\\ 
\hline
&Mesh dens. & \\
&vert/\AA$^2$ & \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 2 & -36.239\\
Standard    & 4  & -33.129 \\
FEM-BEM    & 8  & -32.674 \\
    & 12 & -32.648 \\
    & 16 & -32.293 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
    & 2 & -35.333\\
Hybrid    & 4  & -33.079 \\
FEM-BEM    & 8  & -32.660 \\
    & 12 & -32.587 \\
    & 16 & -32.359 \\
\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS.}
\label{table:arg_variable}
\end{table}

>>>>

\begin{itemize}
\item Do we really need to compute the vacuum case numerically? We should be able to do it analytically, right?
\item Run BEM-BEM with the non regularized version.
\end{itemize}

\begin{figure}
\centering
   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_time.png}
\caption{Time-to-solution for arginine with a constant permittivity. %(1) fix title, (2) can we put them in a single plot, (3) 
maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
\label{fig:arg_contant_time}
\end{figure}

@@

We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS for comparison. 
We chose APBS because it provides an easy interface to control de dielectric map.....
As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, however, the solvent permittivity was set to $\epsilon$=2. 
Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff [Alexov]. 
We did not consider a cutoff in our calculations, but this does not affect our validation exercise.

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
&Mesh size & $\Delta G_{solv}$\\
&\AA       &  kcal/mol \\
\hline
\multirow{3}{*}{APBS}& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
&0.26$\times$0.26$\times$0.26 & -32.3375\\ 
&0.17$\times$0.17$\times$0.17 & -32.3413\\ 
& FINER & If possible\\ 
\hline
&Mesh dens. & \\
&vert/\AA$^2$ & \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 2 & -36.239\\
Standard    & 4  & -33.129 \\
FEM-BEM    & 8  & -32.674 \\
    & 16 & -32.293 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
    & 2 & -35.333\\
Hybrid    & 4  & -33.079 \\
FEM-BEM    & 8  & -32.660 \\
    & 16 & -32.359 \\
\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS. Add performance result?}
\label{table:arg_variable}
\end{table}
